---
title: "Coca-Cola Stocks"
---

How can we use data to determine how much Coca Cola Company stocks will grow and ultimately, should we start investing in COKE!?????!?!?!?!?!?!?!?!?
The data used is by YAHOO!!!! Finance through excel.

I started off by organizing the variables so that we can see how the date connects to the price of the stocks by year. now we can determine if Coca Cola Stocks have a good trend line and it's safe to say that soon, there may be a drop again but it will definitely rise back up in around 10-20 years.              


```{r Coke-Stock-Prices}
#| echo: False
#| message: False
#| warning: False

library(tidyverse)
library(readxl)
library(ggplot2)
library(plotly)

my_data <- read_excel("COCO_COLA.xlsx")

p <- ggplot(data = my_data, # Selects the data to analyze
            mapping = aes(x = Date, 
                          y = High)) + # This sets the x and y axis
        geom_line() + # Creates the line
        labs(y = "$DOLLA$", 
             x = "Year",
             title = "Coca-Cola Stock Price Over the Last Few Years",
             subtitle = "The Coca-Cola Company seems to be having a good trend line.",
             caption = "Coca-Cola stocks from 19 Jan 1962 to 19 Dec 2021 used with Yahoo Finance") 
# Labs to label the titles and everything

ggplotly(p) # This is to make it so that you can zoom into certain sections

 

```


Let's see some other stocks to compare.

```{r}
#| echo: False
#| message: False
#| warning: False

library(tidyverse)
library(readxl)
library(ggplot2)
library(plotly)

my_data <- read_excel("Pepsi_Stock_Data.xlsx")


ggplot(data = my_data, 
            mapping = aes(x = Date, 
                          y = High)) + 
        geom_line() +
        labs(y = "$DOLLA$", 
             x = "Year",
             title = "Pepsi Stocks have a really good compound trend line!",
             caption = "Pepsi stocks used with Macro Trends")
# everything except that it's Pepsi
```


